### 2014-02-01 src/paper.Rnw
udate names

<<prepare,echo=F>>=
attach(m)
sdl_f <- mut.avg~mut.avg.sdl + 0
rnd_f <- mut.avg~mut.avg.rnd + 0

@@

sdl.est <- sdl_s$coefficients['mut.avg.sdl','Estimate']
rnd.est <- rnd_s$coefficients['mut.avg.rnd','Estimate']

@@

\begin{figure*}[t]
<<mutnum, fig.width=5, fig.height=5, out.width='.45\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
hist(log(10,m$pit.mutation.total.sdl), breaks=50, col=rgb(0,0,1,1/4), main='histogram of log(sdl) mutation score')
hist(log(10,m$pit.mutation.num.sdl), breaks=50, add=T, col=rgb(1,0,0,1/4))

hist(log(10,m$pit.mutation.total.rnd), breaks=50, col=rgb(0,0,1,1/4), main='histogram of log(rnd) mutation score')
hist(log(10,m$pit.mutation.num.rnd), breaks=50, add=T, col=rgb(1,0,0,1/4))

@@

\subsubsection{mut.avg.sdl and mut.avg}

<<>>=
c <- cor(subset(m, select=c(mut.avg.sdl, mut.avg)) , method="kendall", use="pairwise")['mut.avg.sdl', 'mut.avg']
d <- cor(subset(m, select=c(mut.avg.rnd, mut.avg)) , method="kendall", use="pairwise")['mut.avg.rnd', 'mut.avg']
@

@@

\subsubsection{mut.avg.rnd and mut.avg}

@@

<<>>=
s <- t.test(mut.avg.rnd, mut.avg.sdl, paired=T)
@

@@

$ \mu_\{M_{all} | M_{sdl}, M_{rnd}\} = 0 + \beta_1 {sdl} + \beta_2 M_{rnd} + \beta_3 M_{sdl} M_{rnd}  $
<<results='asis'>>=
s <- subset(m, select=c(mut.avg,mut.avg.sdl))
s$type <- 'sdl'
colnames(s) <- c('mut', 'sample', 'type')
r <- subset(m, select=c(mut.avg,mut.avg.rnd))
r$type <- 'rnd'
colnames(r) <- c('mut', 'sample', 'type')
all <- rbind(s, r)
detach(m)
fm <- with(all, lm(mut ~ sample + type + sample:type))
sm <- anova(fm)
xtable(sm)
@

@@

We see from the data that random sampling has a higher $R^2$, and also approximates the all  mutations score better.
However, caveat emptor. There is a difference between the number of mutators for SDL and RAND. If our approximation was right, we should have gotten nearly same number of mutators. However
The number of mutators in RND is
 \Sexpr{sum(m$pit.mutation.total.rnd) / sum(m$pit.mutation.total.sdl)} times SDL.

The total mutants for all is \Sexpr{sum(m$pit.mutation.total)}, for rnd is \Sexpr{sum(m$pit.mutation.total.rnd)} and for sdl is \Sexpr{sum(m$pit.mutation.total.sdl)}

>>>>

<<prepare,echo=F>>=
attach(m)
sdl_f <- mut.avg~sdl.mut.avg + 0
rnd_f <- mut.avg~lrnd.mut.avg + 0

@@

sdl.est <- sdl_s$coefficients['sdl.mut.avg','Estimate']
rnd.est <- rnd_s$coefficients['lrnd.mut.avg','Estimate']

@@

\begin{figure*}[t]
<<mutnum, fig.width=5, fig.height=5, out.width='.45\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
hist(log(10,m$sdl.pit.mutation.total), breaks=50, col=rgb(0,0,1,1/4), main='histogram of log(sdl) mutation score')
hist(log(10,m$sdl.pit.mutation.num), breaks=50, add=T, col=rgb(1,0,0,1/4))

hist(log(10,m$lrnd.pit.mutation.total), breaks=50, col=rgb(0,0,1,1/4), main='histogram of log(rnd) mutation score')
hist(log(10,m$lrnd.pit.mutation.num), breaks=50, add=T, col=rgb(1,0,0,1/4))

@@

\subsubsection{sdl.mut.avg and mut.avg}

<<>>=
c <- cor(subset(m, select=c(sdl.mut.avg, mut.avg)) , method="kendall", use="pairwise")['sdl.mut.avg', 'mut.avg']
d <- cor(subset(m, select=c(lrnd.mut.avg, mut.avg)) , method="kendall", use="pairwise")['lrnd.mut.avg', 'mut.avg']
@

@@

\subsubsection{lrnd.mut.avg and mut.avg}

@@

<<>>=
s <- t.test(lrnd.mut.avg, sdl.mut.avg, paired=T)
@

@@

$ \mu_\{M_{all} | M_{sdl}, M_{rnd}\} = 0 + \beta_1 {sdl} + \beta_2 M_{rnd} + \beta_3 M_{sdl} M_{rnd}  $
\begin{small}
<<results='asis'>>=
s <- subset(m, select=c(mut.avg,sdl.mut.avg))
s$type <- 'sdl'
colnames(s) <- c('mut', 'sample', 'type')
r <- subset(m, select=c(mut.avg,lrnd.mut.avg))
r$type <- 'rnd'
colnames(r) <- c('mut', 'sample', 'type')
all <- rbind(s, r)
detach(m)
fm <- with(all, lm(mut ~ sample + type + sample:type))
sm <- anova(fm)
print(xtable(sm,caption="My caption"), size="\\small")
@
\end{small}

@@

We see from the data that random sampling has a higher $R^2$, and also approximates the all  mutations score better.
However, caveat emptor. There is a difference between the number of mutators for SDL and RAND. If our approximation was right, we should have gotten nearly same number of mutators. However
The number of mutators in RND is
 \Sexpr{sum(m$lrnd.pit.mutation.total) / sum(m$sdl.pit.mutation.total)} times SDL.

The total mutants for all is \Sexpr{sum(m$pit.mutation.total)}, for rnd is \Sexpr{sum(m$lrnd.pit.mutation.total)} and for sdl is \Sexpr{sum(m$sdl.pit.mutation.total)}
